Non-kissing complexes and tau-tilting for gentle algebras

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
problems compilation

\begin{table}
	\capstart{}
    \centerline{
    \begin{tabular}{|c|c|c|}
    \hline
    String modules on~$\bar Q$ &
    Walks on~$\bar Q\blossom$  &
    Reference
    \\ \hline \hline
    almost positive strings (Def.~\ref{def:stringsBands}) &
    bending walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    ?\footnotemark[1] &
    straight walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    \multiLinesBox{$P(v)$ and $P(v)[1]$ \\ $A=kQ/I$ and~$A[1]$ \\ ~} &
    \multiLinesBox{$v_\peak$ and $v_\deep$ \\ $F_\peak$ and~$F_\deep$ \\ (Exm.~\ref{example: Fdeep Fpeak} and Def.~\ref{def: deep walk})} &
    Lem.~\ref{lem:bijections-STTC-NKC}
    \\ \hline
    ?\footnotemark[2] &
    countercurrent order~$\prec_\alpha$ &
    ---
    \\ \hline
    $\tau$-compatibility (Def.~\ref{def: tau-compatibility}) &
    non-kissing (Def.~\ref{def: kissing}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting object (Def.~\ref{def: tau-rigid and stautilt}) &
    maximal non-kissing collection of walks &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting complex~$\tTC$ (Def.~\ref{def: stautilt complex}) &
    reduced non-kissing complex~$\RNKC$ (Def.~\ref{def: nKc}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm: mutation of stautilts}~\cite{AdachiIyamaReiten})} &
    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    lattice of torsion classes &
    non-kissing lattice~$\NKL$ (Thm.~\ref{thm:lattice}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    bricks &
    \multiLinesBox{distinguishable strings (Def.~\ref{def:distinguishedSubstring})} &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    collections of pairwise Hom-orthogonal bricks &
    non-friendly complex (Def.~\ref{def: friendly}) &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    \multiLinesBox{bijection between indecomposable~$\tau$-rigid representations and bricks (Thm. 6.1 in~\cite{DemonetIyamaJasso})} &
    \multiLinesBox{bijection between non-kissing walks that are not peak walks and distinguishable strings (Prop.~\ref{prop:bijectionDistinguishableStringsWalks})} &
    \multiLinesBox{Conjectural \\ cf.~Prop.~\ref{prop:bijectionDistinguishableStringsJI}}[2cm]
    \\ \hline
    \multiLinesBox{Bongartz cocompletion of a~$\tau$-rigid indecomposable representation $N=M(\rho)$ whose associated brick is~$M(\sigma)$. Moreover $\sigma = \distinguishedWalk{\omega(\rho)}{F}$} &
    \multiLinesBox{$F=\eta\left(\closure{\Sigma_\bottom(\sigma)}\right)$, where $\sigma$ is a distinguishable string} &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    Bongartz completion &
    $\eta\left(\closure{\Sigma_\top(\sigma)}\right)$ &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    $\b{g}$-vector or index of a module (Def.~\ref{definition: g-vector of representation}) &
    $\b{g}$-vector of a walk (Def.~\ref{def: g-vectors for walks}) &
    Rem.~\ref{rem: g-vectors coincide}
    \\ \hline
    $\dim \Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$ (Sec.~\ref{subsec:tautilting}) &
    kissing number~$\kappa \big( \omega(\sigma), \omega(\sigma') \big)$ (Def.~\ref{def: kissing number}) &
    Rem.~\ref{rem:KNvsTau}
    \\ \hline
    \end{tabular}
    }
    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
    \label{table:dictionary}    
\end{table}

@@

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, Proposition~\ref{prop: nk facets are finite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.

\begin{lemma}\label{lemma: distinguished arrows exists}
Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
\end{lemma}

@@

\begin{proposition}\label{prop: nk facets are finite}
The faces of the non-kissing complex have finite cardinality.
\end{proposition}

\begin{proof}
By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
% Let~$F$ be a non-kissing face.
% Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
% Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
% Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
% Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
% Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
% This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
% Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
% Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
% If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
% Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
% If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
% Hence,~$\mu$ kisses itself, which is absurd.
% Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.
\end{proof}

@@

\begin{proof}
The theorem is a direct consequence of Lemma~\ref{lem: attract or dance vs kiss}, except for the fact that increasing flips correspond to left mutations.
We use the notation of Proposition~\ref{prop:flip} and Figure~\ref{fig:flip}: let $F$ and~$F'$ be two adjacent facets such that the flip of~$F$ to~$F'$ is increasing, let $\omega$ and~$\omega'$ are the walks such that~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, let~$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ and~$\{\alpha', \beta'\} = \distinguishedArrows{\omega'}{F'}$, let~$\xi = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$, and let~$\mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}$ and~$\nu = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\alpha}{F'}$.
We consider the four associated strings~$\sigma(\omega), \sigma(\omega'), \sigma(\mu)$ and~$\sigma(\nu)$.
Note that~$\mu$ could be a straight walk, in which case we let~$\sigma(\mu)$ be~$\varnothing$ so that~$M \big( \sigma(\mu) \big) = 0$, and similarly for~$\nu$.
Since the statement is trivially satisfied when~$\omega'$ is a deep walk, we may assume that it is not the case.
We claim that the representation~$M \big( \sigma(\omega') \big)$ is a quotient of~$M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big)$, which implies the statement by~\cite[Def.--Prop.~2.28]{AdachiIyamaReiten}.
First note that the distinguished string~$\xi$ is also a substring of~$\omega$ (use~$\alpha$ and~$\beta$).
We distinguish five cases, depending on which of the distinguished arrows~$\alpha'$ and~$\beta'$ belongs to some cohook in~$\omega'$.
Assuming first that~$\alpha', \beta'$ both belong to~$\sigma(\omega')$, then there is a short exact sequence~$0\rightarrow M \big( \sigma(\omega) \big) \rightarrow M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big) \rightarrow 0$.
Assume next that~$\alpha'$ belongs to some (left) cohook for~$\omega'$, but that~$\beta'$ belongs to~$\sigma(\omega')$.
This implies that~$\nu$ is not a straight walk and that~$\sigma(\omega')$ is a substring on top of~$\sigma(\nu)$, thus giving a sujection~$M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big)$.
The symmetric case gives a surjection~$M \big( \sigma(\mu) \big) \rightarrow M \big( \sigma(\omega') \big)$.
Assume that the distinguished arrows~$\alpha', \beta'$ both belong to the same cohook.
By symmetry, we may assume that it is a left cohook.
In that case again,~$\nu$ is not a straight walk and~$\sigma(\omega')$ is a substring on top of~$\sigma(\nu)$.
Finally, assuming that~$\alpha'$ belongs to some left cohook, while~$\beta'$ belongs to some right cohook for~$\omega'$, the string~$\sigma(\omega')$ is easily seen to be on top of both strings~$\sigma(\mu)$ and~$\sigma(\nu)$.
\end{proof}

@@

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S)$}
			\put(50,-3){$S$}
			\put(85,-3){$\projUp(S)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q\}$ (middle), where~$\bar Q$ is the bound quiver of~\fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}

>>>>

\begin{table}
	\capstart{}
    \centerline{
    \begin{tabular}{|c|c|c|}
    \hline
    String modules on~$\bar Q$ &
    Walks on~$\bar Q\blossom$  &
    Reference
    \\ \hline \hline
    almost positive strings (Def.~\ref{def:stringsBands}) &
    bending walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    ?\footnotemark[1] &
    straight walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    \multiLinesBox{$P(v)$ and $P(v)[1]$ \\ $A=kQ/I$ and~$A[1]$ \\ ~} &
    \multiLinesBox{$v_\peak$ and $v_\deep$ \\ $F_\peak$ and~$F_\deep$ \\ (Exm.~\ref{example: Fdeep Fpeak} and Def.~\ref{def: deep walk})} &
    Lem.~\ref{lem:bijections-STTC-NKC}
    \\ \hline
    ?\footnotemark[2] &
    countercurrent order~$\prec_\alpha$ &
    ---
    \\ \hline
    $\tau$-compatibility (Def.~\ref{def: tau-compatibility}) &
    non-kissing (Def.~\ref{def: kissing}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting object (Def.~\ref{def: tau-rigid and stautilt}) &
    maximal non-kissing collection of walks &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting complex~$\tTC$ (Def.~\ref{def: stautilt complex}) &
    reduced non-kissing complex~$\RNKC$ (Def.~\ref{def: nKc}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm:mutationstautilts}~\cite{AdachiIyamaReiten})} &
    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    lattice of torsion classes &
    non-kissing lattice~$\NKL$ (Thm.~\ref{thm:lattice}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    bricks &
    \multiLinesBox{distinguishable strings (Def.~\ref{def:distinguishedSubstring})} &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    collections of pairwise Hom-orthogonal bricks &
    non-friendly complex (Def.~\ref{def: friendly}) &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    \multiLinesBox{bijection between indecomposable~$\tau$-rigid representations and bricks (Thm. 6.1 in~\cite{DemonetIyamaJasso})} &
    \multiLinesBox{bijection between non-kissing walks that are not peak walks and distinguishable strings (Prop.~\ref{prop:bijectionDistinguishableStringsWalks})} &
    \multiLinesBox{Conjectural \\ cf.~Prop.~\ref{prop:bijectionDistinguishableStringsJI}}[2cm]
    \\ \hline
    \multiLinesBox{Bongartz cocompletion of a~$\tau$-rigid indecomposable representation $N=M(\rho)$ whose associated brick is~$M(\sigma)$. Moreover $\sigma = \distinguishedWalk{\omega(\rho)}{F}$} &
    \multiLinesBox{$F=\eta\left(\closure{\Sigma_\bottom(\sigma)}\right)$, where $\sigma$ is a distinguishable string} &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    Bongartz completion &
    $\eta\left(\closure{\Sigma_\top(\sigma)}\right)$ &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    $\b{g}$-vector or index of a module (Def.~\ref{definition: g-vector of representation}) &
    $\b{g}$-vector of a walk (Def.~\ref{def: g-vectors for walks}) &
    Rem.~\ref{rem: g-vectors coincide}
    \\ \hline
    $\dim \Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$ (Sec.~\ref{subsec:tautilting}) &
    kissing number~$\kappa \big( \omega(\sigma), \omega(\sigma') \big)$ (Def.~\ref{def: kissing number}) &
    Rem.~\ref{rem:KNvsTau}
    \\ \hline
    \end{tabular}
    }
    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
    \label{table:dictionary}    
\end{table}

@@

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, Proposition~\ref{prop:nkFacetsAreFinite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.

\begin{lemma}\label{lem:distArrowExist}
Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
\end{lemma}

@@

\begin{proposition}\label{prop:nkFacetsAreFinite}
The faces of the non-kissing complex have finite cardinality.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:distArrowExist}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
% Let~$F$ be a non-kissing face.
% Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
% Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
% Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
% Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
% Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
% This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
% Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
% Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
% If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
% Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
% If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
% Hence,~$\mu$ kisses itself, which is absurd.
% Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.
\end{proof}

@@

\begin{proof}
The theorem is a direct consequence of Lemma~\ref{lem:attractDanceKiss}, except for the fact that increasing flips correspond to left mutations.
We use the notation of Proposition~\ref{prop:flip} and Figure~\ref{fig:flip}: let $F$ and~$F'$ be two adjacent facets such that the flip of~$F$ to~$F'$ is increasing, let $\omega$ and~$\omega'$ are the walks such that~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, let~$\{\alpha, \beta\} = \distinguishedArrows{\omega}{F}$ and~$\{\alpha', \beta'\} = \distinguishedArrows{\omega'}{F'}$, let~$\xi = \distinguishedString{\omega}{F} = \distinguishedString{\omega'}{F'}$, and let~$\mu = \distinguishedWalk{\alpha'}{F} = \distinguishedWalk{\beta}{F'}$ and~$\nu = \distinguishedWalk{\beta'}{F} = \distinguishedWalk{\alpha}{F'}$.
We consider the four associated strings~$\sigma(\omega), \sigma(\omega'), \sigma(\mu)$ and~$\sigma(\nu)$.
Note that~$\mu$ could be a straight walk, in which case we let~$\sigma(\mu)$ be~$\varnothing$ so that~$M \big( \sigma(\mu) \big) = 0$, and similarly for~$\nu$.
Since the statement is trivially satisfied when~$\omega'$ is a deep walk, we may assume that it is not the case.
We claim that the representation~$M \big( \sigma(\omega') \big)$ is a quotient of~$M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big)$, which implies the statement by~\cite[Def.--Prop.~2.28]{AdachiIyamaReiten}.
First note that the distinguished string~$\xi$ is also a substring of~$\omega$ (use~$\alpha$ and~$\beta$).
We distinguish five cases, depending on which of the distinguished arrows~$\alpha'$ and~$\beta'$ belongs to some cohook in~$\omega'$.
Assuming first that~$\alpha', \beta'$ both belong to~$\sigma(\omega')$, then there is a short exact sequence~$0\rightarrow M \big( \sigma(\omega) \big) \rightarrow M \big( \sigma(\mu) \big) \oplus M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big) \rightarrow 0$.
Assume next that~$\alpha'$ belongs to some (left) cohook for~$\omega'$, but that~$\beta'$ belongs to~$\sigma(\omega')$.
This implies that~$\nu$ is not a straight walk and that~$\sigma(\omega')$ is a substring on top of~$\sigma(\nu)$, thus giving a sujection~$M \big( \sigma(\nu) \big) \rightarrow M \big( \sigma(\omega') \big)$.
The symmetric case gives a surjection~$M \big( \sigma(\mu) \big) \rightarrow M \big( \sigma(\omega') \big)$.
Assume that the distinguished arrows~$\alpha', \beta'$ both belong to the same cohook.
By symmetry, we may assume that it is a left cohook.
In that case again,~$\nu$ is not a straight walk and~$\sigma(\omega')$ is a substring on top of~$\sigma(\nu)$.
Finally, assuming that~$\alpha'$ belongs to some left cohook, while~$\beta'$ belongs to some right cohook for~$\omega'$, the string~$\sigma(\omega')$ is easily seen to be on top of both strings~$\sigma(\mu)$ and~$\sigma(\nu)$.
\end{proof}

@@

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S)$}
			\put(50,-3){$S$}
			\put(85,-3){$\projUp(S)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q}$ (middle), where~$\bar Q$ is the bound quiver of~\fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}
